Object-Oriented Internet - Azure Interoperability

### 2020-12-01 Latex/Manuscript.tex
Update 2.1 Architecture
> Unlike the above described solutions, the \textbf{embedded gateway} is not derived from the middleware concept.

How do we define middleware? One could say that all three kinds of devices act as in-between agents translating data, including the embedded gateway.

> As a result, any product being advertised as Industry 4.0 enabled must be OPC UA-capable somehow

Does OPC UA really have a monopoly on being Industry 4.0 compliant? You mentioned some solution from India lately... Assuming the range of Industry 4.0 solutions must all be interoperable I'd reword it to make

Interconnection of the reactive \textbf{machine - centric} and interactive \textbf{human - centric} environments can be implemented by applying one of the following scenarios:

@@

The possibility to establish a common semantic-context in the multi-vendor environment makes communication standardization especially important. In this case, it is required that the encoding of the messages payload exchanged over the network (Data Transfer Object - TDO) is standardized so that the payload can be factored on the data-gathering site and consumed on the ultimate destination data processing sites. Security between the data origin and ultimate data destination refers to the protection of messages (security-context) against malicious users. It is required that communicating parties are using the same cyber-security measures.

@@

The virtualization of cloud services means that they must be very flexible to handle the attachment of new assets proactively (acting in advance) at run time. As a result, by design, the cloud services must be repressible to register and authenticate devices exposing endpoints in the public network to allows the device to access a provisioning cloud service. It requires that a session over the Internet has to be established by the data holding asset at a preparation step.

>>>>

Interconnection of the reactive \textbf{machine-centric} and interactive \textbf{human-centric} environments can be implemented by applying one of the following scenarios:

@@

The possibility to establish a common semantic-context in the multi-vendor environment makes communication standardization especially important. In this case, it is required that the encoding of the messages payload exchanged over the network (Data Transfer Object - DTO) is standardized so that the payload can be factored on the data-gathering site and consumed on the ultimate destination data processing sites. Security between the data origin and ultimate data destination refers to the protection of messages (security-context) against malicious users. It is required that communicating parties are using the same cyber-security measures.

@@

The virtualization of cloud services means that they must be very flexible to handle the attachment of new assets proactively (acting in advance) at run time. As a result, by design, the cloud services must be responsible to register and authenticate devices by exposing endpoints in the public network to allow the device to access a provisioning cloud service. It requires that a session over the Internet has to be established by the data holding asset at a preparation step.
